Analysis of HTTPS Adoption and Third-party Tracking: \\A Swedish Perspective

### 2015-05-04 paper/figures.tex
Fix x axis label
Adjusted/scaled 2xx/3xx results

@@

\YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpsWww}{2xx}{2xx}{green}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpsWww}{3xx}{3xx}{yellow}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpsWww}{(null)}{(null)}{red}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mix sec}{3xx Mix}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Insec}{3xx Insec}{red}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}{Mism}{3xx Mismatch}{lightgray}{}

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww;
\addlegendentry{3xx Final sec}

@@

\YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpsWww}{2xx}{2xx}{green}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpsWww}{3xx}{3xx}{yellow}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpsWww}{(null)}{(null)}{red}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mix sec}{3xx Mix}{orange}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Insec}{3xx Insec}{red}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}{Mism}{3xx Mismatch}{lightgray}{}

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww;
\addlegendentry{3xx Final sec}

@@

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww}{2xx}{2xx}{green}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww}{3xx}{3xx}{yellow}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww}{(null)}{(null)}{red}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Mix sec}{3xx Mix}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Insec}{3xx Insec}{orange}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}{Mism}{3xx Mismatch}{lightgray}{}

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww;
\addlegendentry{3xx Final sec}

@@

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww}{2xx}{2xx}{green}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww}{3xx}{3xx}{yellow}{}

% \YBarPlotFromDataset{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww}{(null)}{(null)}{red}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Mix sec}{3xx Mix}{yellow}{}

\YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Insec}{3xx Insec}{orange}{}

% \YBarPlotFromDataset{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}{Mism}{3xx Mismatch}{lightgray}{}

\addplot+[
		stack plots=false,
		only marks,
		mark=x,
		mark size=3pt,
		fill=white,
		draw=black,
		thick,
		fill opacity=1,
		update limits=false,
		line legend,
	]
	table[y=Final sec,x=Dataset]
	\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww;
\addlegendentry{3xx Final sec}

@@

\tikzsetnextfilename{mini-1x1-secure-resources-cdf}
\begin{tikzpicture}
\begin{axis}[
	% title=(b) Secure resources,
	datasetsCDF,
	datasetsCDFMiniResults,
	paperTight,
	xlabel=Ratio of internal resources,
	ylabel=Ratio of domains,
	legend style={at={(1.03,.5)}, anchor=west},
	xlabel style={
		at={(0.5,0.1)}
	},
	ylabel style={
		at={(0.17,0.5)}
	},
]

>>>>

\createAdjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedHttpsWww{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpsWww}{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpsWww}{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpsWww}
\createAdjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedHttpsWww{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpsWww}{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpsWww}{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpsWww}
\createAdjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedHttpWww{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpWww}{\tableDatasetsRequestStatusCoverageOriginSortedSwedenHttpWww}{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedSwedenHttpWww}
\createAdjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedHttpWww{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpWww}{\tableDatasetsRequestStatusCoverageOriginSortedGlobalHttpWww}{\tableDatasetsNonFailedClassificationOriginRedirectsCoverageSortedGlobalHttpWww}

@@

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpsWww}{2xx}{2xx}{green}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpsWww}{3xx Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpsWww}{3xx Mix sec}{3xx Mix}{orange}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpsWww}{3xx Insec}{3xx Insec}{red}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpsWww}{3xx Mism}{3xx Mism}{lightgray}{}

@@

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpsWww}{2xx}{2xx}{green}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpsWww}{3xx Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpsWww}{3xx Mix sec}{3xx Mix}{orange}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpsWww}{3xx Insec}{3xx Insec}{red}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpsWww}{3xx Mism}{3xx Mism}{lightgray}{}

@@

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpWww}{3xx Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpWww}{3xx Mix sec}{3xx Mix}{yellow}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpWww}{3xx Insec}{3xx Insec}{orange}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedSwedenHttpWww}{3xx Mism}{3xx Mism}{lightgray}{}

@@

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpWww}{3xx Sec}{3xx Sec}{green!30!yellow}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpWww}{3xx Mix sec}{3xx Mix}{yellow}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpWww}{3xx Insec}{3xx Insec}{orange}{}

\YBarPlotFromDataset{\adjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedGlobalHttpWww}{3xx Mism}{3xx Mism}{lightgray}{}

@@

\tikzsetnextfilename{mini-1x1-secure-resources-cdf}
\begin{tikzpicture}
\begin{axis}[
	% title=(b) Secure resources,
	datasetsCDF,
	datasetsCDFMiniResults,
	paperTight,
	xlabel=Ratio of secure resources,
	ylabel=Ratio of domains,
	legend style={at={(1.03,.5)}, anchor=west},
	xlabel style={
		at={(0.5,0.1)}
	},
	ylabel style={
		at={(0.17,0.5)}
	},
]

### 2015-05-04 paper/tableread.tex
Adjusted/scaled 2xx/3xx results

>>>>

\newcommand{\createAdjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedHttpsWww}[3]{
	\pgfplotstableset{
		create on use/Dataset/.style={create col/copy column from table={#2}{Dataset}},%
		create on use/2xx Raw/.style={create col/copy column from table={#2}{2xx}},%
		create on use/3xx Raw/.style={create col/copy column from table={#2}{3xx}},%
		create on use/3xx Sec Raw/.style={create col/copy column from table={#3}{Sec}},%
		create on use/3xx Mix sec Raw/.style={create col/copy column from table={#3}{Mix sec}},%
		create on use/3xx Insec Raw/.style={create col/copy column from table={#3}{Insec}},%
		create on use/3xx Mism Raw/.style={create col/copy column from table={#3}{Mism}},%
		create on use/3xx Final sec Raw/.style={create col/copy column from table={#3}{Final sec}},%
	}

	\pgfplotstablenew[
		columns={
			Dataset,%
			2xx Raw,%
			3xx Raw,%
			3xx Sec Raw,%
			3xx Mix sec Raw,%
			3xx Insec Raw,%
			3xx Mism Raw,%
			3xx Final sec Raw,%
			Total Scale,%
			2xx,%
			3xx Sec,%
			3xx Mix sec,%
			3xx Insec,%
			3xx Mism,%
			3xx Final sec%
		},
		create on use/Total Scale/.style={create col/expr={1/(\thisrow{2xx Raw}+\thisrow{3xx Raw})}},%
		create on use/2xx/.style={create col/expr={\thisrow{2xx Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Sec/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Sec Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Mix sec/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Mix sec Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Insec/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Insec Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Mism/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Mism Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Final sec/.style={create col/expr={(\thisrow{2xx Raw}+\thisrow{3xx Raw}*\thisrow{3xx Final sec Raw})*\thisrow{Total Scale}}},%
	]{\pgfplotstablegetrowsof{#2}}#1%
}

\newcommand{\createAdjustedTableDatasetsRequestStatusCoverageOriginRedirectSecuritySortedHttpWww}[3]{
	\pgfplotstableset{
		create on use/Dataset/.style={create col/copy column from table={#2}{Dataset}},%
		create on use/3xx Raw/.style={create col/copy column from table={#2}{3xx}},%
		create on use/3xx Sec Raw/.style={create col/copy column from table={#3}{Sec}},%
		create on use/3xx Mix sec Raw/.style={create col/copy column from table={#3}{Mix sec}},%
		create on use/3xx Insec Raw/.style={create col/copy column from table={#3}{Insec}},%
		create on use/3xx Mism Raw/.style={create col/copy column from table={#3}{Mism}},%
		create on use/3xx Final sec Raw/.style={create col/copy column from table={#3}{Final sec}},%
	}

	\pgfplotstablenew[
		columns={
			Dataset,%
			3xx Raw,%
			3xx Sec Raw,%
			3xx Mix sec Raw,%
			3xx Insec Raw,%
			3xx Mism Raw,%
			3xx Final sec Raw,%
			Total Scale,%
			3xx Sec,%
			3xx Mix sec,%
			3xx Insec,%
			3xx Mism,%
			3xx Final sec%
		},
		create on use/Total Scale/.style={create col/expr={1/\thisrow{3xx Raw}}},%
		create on use/3xx Sec/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Sec Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Mix sec/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Mix sec Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Insec/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Insec Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Mism/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Mism Raw}*\thisrow{Total Scale}}},%
		create on use/3xx Final sec/.style={create col/expr={\thisrow{3xx Raw}*\thisrow{3xx Final sec Raw}*\thisrow{Total Scale}}},%
	]{\pgfplotstablegetrowsof{#2}}#1%
}
